Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-02-28 docs/Truman/LocalConservation/paper.tex
Added Hemker results to paper.

>>>>

\subsection{Hemker Problem}
The Hemker problem is defined on a domain
$\Omega=\{[-3,9]\times[-3,3]\}\{(x,y):x^2+y^2<1\}$, essentially a simplified
model of flow past an infinite cylinder. We start with the initial mesh shown
in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 32
linear segments. Our code does not fully support curvilinear elements at this
time, so as we refine, we just subdivide the initial linear segments. The
boundary conditions are $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left
inflow boundary, $\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the
right outflow boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$
on the cylinder.

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
\caption{Initial mesh for the Hemker problem}
\label{fig:hemkerInitial}
\end{figure}

After some early refinement steps in which the graph norm solutions exhibit
some strange behavior (see Figure~\ref{fig:hemker4}) all four methods appear
to converge toward a decent solution as shown in Figure~\ref{fig:hemker8}. The
different methods seem to prioritize different parts of the mesh for
refinement, but with sufficient refinement, the differences in the actual
solution are fairly insignificant. TODO: Explain why $\hat u$ boundary is not
nice on inflow.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph4nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph4nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:hemkerGraph14nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust4nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust4nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:hemkerRobust14nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph4c.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph4c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:hemkerGraph14c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust4c.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust4c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:hemkerRobust14c}
\end{subfigure}
\caption{Hemker problem after 4 refinements}
\label{fig:hemker4}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph8nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph8nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:hemkerGraph18nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust8nc.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust8nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:hemkerRobust18nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graph8c.png}
\includegraphics[width=\textwidth]{figs/Hemker/graph8c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:hemkerGraph18c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robust8c.png}
\includegraphics[width=\textwidth]{figs/Hemker/robust8c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:hemkerRobust18c}
\end{subfigure}
\caption{Hemker problem after 8 refinements}
\label{fig:hemker8}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graphFlux.pdf}
\caption{With graph norm}
\label{fig:hemkerGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robustFlux.pdf}
\caption{With robust norm}
\label{fig:hemkerRobustFlux}
\end{subfigure}
\caption{Flux imbalance in Hemker solutions}
\label{fig:hemker_flux}
\end{figure}
